---
title: "Final Report"
output: tint::tintHtml
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(ggalluvial)


# load your data here 
load("data/explore_forthright.RData")
#load("data/") # for YouGov
```

### Introduction 

This project, PATHS to disinformation, analyzed two data sets provided by YouGov (370 participants) and Forthright (584 participants) that track the browsing history of the participants. The aims for this analysis was to track the digital pathways of these individuals, identify the online platforms that lead them to disinformation, and interpret the relationship between those individuals and their political afflitaiton, which was also provided by our data.  

### Methodology

We use 

### Visualizations

#### Forthright dataset
```{r}

# code goes here to make the alluvial diagrams of disinformation visit
top3 <- explore_forthright %>% 
  group_by(prev_domain, next_domain, slant, disinformation) %>% 
  tally()

ggplot(top3 %>% filter( prev_domain != "non", next_domain != "non", disinformation != "non"), aes(axis1 = prev_domain, axis2 = disinformation, axis3=next_domain, y = n)) +
  geom_alluvium(aes(fill=slant)) +
  scale_fill_manual( values = c("blue", "grey", "red") ) +
  geom_stratum() +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  scale_x_discrete(limits = c("Previous", "Current", "Next"), expand = c(0.15, 0.05)) +
  theme_minimal() +
  theme(legend.position = "bottom",
        text = element_text(family = "Times New Roman")) + 
  labs(y = "Number of Visits",
       x = "Paths",
       title = "Disinformation Visits",
       fill = "Political affiliation")

# code goes here to make the alluvial diagrams of partisan media visit
paths_2 <- explore_forthright %>% 
  group_by(ideology, axis2, slant) %>% 
  tally()

ggplot(paths_2 %>% drop_na(ideology) %>% filter( axis2 != "non", ideology!="Neutral"), aes(axis1 = ideology, axis2 = axis2, y = n)) +
  geom_alluvium(aes(fill=slant)) +
  scale_fill_manual( values = c("blue", "grey", "red") ) +
  geom_stratum() +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  scale_x_discrete(limits = c("Partisan media", "Disinformation"), expand = c(0.15, 0.05)) +
  theme_minimal() +
  theme(legend.position = "bottom",
        text = element_text(family = "Times New Roman")) + 
  labs(y = "Number of Visits",
       x = "Paths",
       title = "Partisan Media Visits",
       fill = "Political affiliation")
```
ForthWright:
The majority of the digital paths in the ForthWright data set have their starting point at Google, with higher traffic coming from individuals who consider themselves right-wing. For the left-wing individuals, they split into halves after they arrive to CNN, with one half staying there and the other continuing browsing. On the other hand, the right-wing individuals had more consistency in their browsing and news visits. They tend to stay on more on the sites that align with their ideologies, moreover none of them visited opposing disinformation sites after their first visit to their similarly-aligned media.
The partisan media visits show that most of media in the Forthright data set is classified as right-wing media, but its audience media's choice is well-coordinated, as they seem to only visit their biased site.


YouGov:
In the YouGov data set, the paths taken by individuals who consider themselves left-wing were inconsistent and more free-flowing, With the majority of them starting at Facebook, and then moving to Fox News. After that, there is a high percentage of left-wing individuals that stay on Fox News (even more left-wing visits than right-wing at the last column). On the other hand, individuals who consider themselves right-wing are consistent in their online pathways with a small percentage of those individuals visiting CNN.
The partisan media visits from YouGov indicates that there’s more left-aligned media than right-aligned ones. Overall, it still reinforces that right-wing audience is more well-coordinated compared to left-wing audience.


### Conclusion
