---
title: "Final Report"
output: tint::tintHtml
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(ggalluvial)


# load your data here 
load("data/explore_forthright.RData")
#load("data/") # for YouGov
```

### Introduction 

This project, PATHS to disinformation, analyzed two data sets provided by YouGov (370 participants) and Forthright (584 participants) that track the browsing history of the participants. The aims for this analysis was to track the digital pathways of these individuals, identify the online platforms that lead them to disinformation, and interpret the relationship between those individuals and their political afflitaiton, which was also provided by our data.  

### Methodology

We use 

### Visualizations

#### Forthright dataset
```{r}

# code goes here to make the alluvial diagrams of disinformation visit
top3 <- explore_forthright %>% 
  group_by(prev_domain, next_domain, slant, disinformation) %>% 
  tally()

ggplot(top3 %>% filter( prev_domain != "non", next_domain != "non", disinformation != "non"), aes(axis1 = prev_domain, axis2 = disinformation, axis3=next_domain, y = n)) +
  geom_alluvium(aes(fill=slant)) +
  scale_fill_manual( values = c("blue", "grey", "red") ) +
  geom_stratum() +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  scale_x_discrete(limits = c("Previous", "Current", "Next"), expand = c(0.15, 0.05)) +
  theme_minimal() +
  theme(legend.position = "bottom",
        text = element_text(family = "Times New Roman")) + 
  labs(y = "Number of Visits",
       x = "Paths",
       title = "Disinformation Visits",
       fill = "Political affiliation")

# code goes here to make the alluvial diagrams of partisan media visit
paths_2 <- explore_forthright %>% 
  group_by(ideology, axis2, slant) %>% 
  tally()

ggplot(paths_2 %>% drop_na(ideology) %>% filter( axis2 != "non", ideology!="Neutral"), aes(axis1 = ideology, axis2 = axis2, y = n)) +
  geom_alluvium(aes(fill=slant)) +
  scale_fill_manual( values = c("blue", "grey", "red") ) +
  geom_stratum() +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  scale_x_discrete(limits = c("Partisan media", "Disinformation"), expand = c(0.15, 0.05)) +
  theme_minimal() +
  theme(legend.position = "bottom",
        text = element_text(family = "Times New Roman")) + 
  labs(y = "Number of Visits",
       x = "Paths",
       title = "Partisan Media Visits",
       fill = "Political affiliation")
```

The majority of the digital paths in our data sets have their starting point at google, with higher traffic coming from individuals who consider themselves right wing. For the left wing individuals, they split into halves after they arrive to CNN, with one half staying there and the other continuing browsing. On the other hand, the right wing individuals had more consistency in their browsing and news visits. They tend to stay on more on the sites that align with their ideologies, moreover none of them visited opposing disinformation sites after their first visit to their similarly-aligned media.
The partisan media visits show that most of media in the Forthright data set is classified as right wing media, but its audience media's choice is well-coordinated, as they seem to only visit their biased site.


YouGov
In this dataset, left-wing visits are inconsistent and more free-flowing, as the majority of them coming from Facebook, then visit Fox News. After that, there’s still a good amount of left-wing stay on Fox News (even more left-visit than right at the last column). Still, right-wing is consistent with their media choice as not many of them visit CNN.
The partisan media visit’s from YouGov indicates there’s more left wing media than right wing media. Overall, it still reinforces that right-wing audience is more well-coordinated compared to left-wing audience.


### Conclusion
